---
title: "Case Study I - Ramen"
author: "Hadley Dixon"
date: "2022-09-14"
output: html_document
---

**Load the data in the following way:**

```{r}
load("/Users/hadleydixon/Desktop/HADLEY/USF_BSDS100/BSDS100_CaseStudies/BSDS100_CaseStudy1/ramen.RData")
```

**1) (5 pts) How many different brands are reviewed in the data set? Do you recognize any of them?**

There are 355 different brands. No, we don't recognize any of them.
```{r}
length(unique(ramen$Brand))
```

**2) (5 pts) What years do we have “top ten” data from? (Hint: This will require turning the Top Ten column into a string column)**

We have "top ten" data from 2012, 2013, 2014, 2015, and 2016.

```{r}
Top.Ten <- ramen$Top.Ten
Top.Ten.String <- as.character(Top.Ten)
no.blank <- Top.Ten.String[Top.Ten.String != ""]
```

**3) (5 pts) Which ramen brands are from the United States (hint: beware of abbreviations!)?**

The ramen brands from the United States are as follows:
```{r}
Country <- ramen$Country
ramen$Brand[Country == "USA" | Country == "United States"]
```

**4) (5 pts) Has any brand of ramen won the #1 slot in the Top Ten Ramens list more than once? Which brand(s)?**

Yes, there are 2 brands of ramen that have won the #1 slot in the Top Ten Ramen List more than once. These brands are Prima Taste and MyKuali. 

```{r}
ramen$Brand[(substr(ramen$Top.Ten, 7,8)) == "1"]
```

**5) (8 pts) Which brand has the highest average star rating? If there is a tie, report multiple brands.**

The brand with the highest average star rating is ChoripDong, with a 5 stars average rating.

```{r}
averages <- aggregate(ramen$Stars, by = list(ramen$Brand), FUN = mean)
averages$Group.1[which.max(averages$x)]
max(averages$x, na.rm = TRUE)
```

**6) (8 pts) Is the way a ramen is packaged related to which country it is from?**

The highest packaging in a pack is from South Korea. The highest packaging in a tray, cup, can. The highest packaging in a box is from Japan and Malaysia. The Highest packaging in a bowl is from Japan. Only US makes ramen in a Bar packaging. Only the US makes ramen in a can packaging, so if we see that packaging in the data set we can conclude that the brand is from the US.

```{r}
table(ramen$Country, ramen$Style)
```

**7) (8 pts) What is the average, maximum, and minimum rating for ramens from the US? What about for ramens from Singapore? Based on your findings, which country do you expect to land in the Top Ten more often? Check your prediction.**

For the United States ratings, the average is 3.457043, the maximum is 5, and the minimum is 0. For Singapore ratings, the mean is 4.126147, the maximum is 5, and the minimum is 2. From this, I expect Singapore to land in the Top Ten more often. Our prediction is correct.

```{r}
mean(ramen$Stars[ramen$Country == "USA" | ramen$Country == "UnitedStates"]) # 3.457043
max(ramen$Stars[ramen$Country == "USA" | ramen$Country == "UnitedStates"]) # 5
min(ramen$Stars[ramen$Country == "USA" | ramen$Country == "UnitedStates"]) # 0

mean(ramen$Stars[ramen$Country == "Singapore"]) # 4.126147
max(ramen$Stars[ramen$Country == "Singapore"]) # 5
min(ramen$Stars[ramen$Country == "Singapore"]) # 2

# Check my prediction
Top.Ten[ramen$Country == "Singapore"]
Top.Ten[ramen$Country == "USA" | ramen$Country == "UnitedStates"]
```
**8) (8 pts) Which country makes the most ramen? Which country makes the best ramen? How did you define “best”? Why? Was the country that makes the best ramen also the country that makes the most ramen?**

Japan makes the most ramen. 

```{r}
table.country.brand <- table(ramen$Country, ramen$Brand)

rowSums(table.country.brand, na.rm=TRUE)
```

We defined "best" as the countries whose brands have appeared in the Top Ten more than once. The countries which make the "best" ramen are Singapore, Malaysia, and Japan.

```{r}
Topten.twice <- ramen$Brand[(substr(ramen$Top.Ten, 7,8)) == "1"]
Topten.twice

ramen$Country[which(ramen$Brand == "Prima Taste" | ramen$Brand == "MyKuali")]
```

**9) (8 pts) How many ramens are considered spicy as part of their variety (hint, don’t forget that “spicy” and “Spicy” are both spicy)? Are spicy ramens typically rated higher than non-spicy ramens?**

SKIPPED

**10) (10 pts) Based on this data set, what effect does saltiness have on ramen ratings?**

Based on this data set, the higher salt percentage, the better rating of ramen.

```{r}
plot(ramen$perc_salt, ramen$Stars)
```

**11) (10 pts) Are there certain styles, countries, brands, or flavors of ramen that tend to use more or less salt? **

Brazil uses the most salt, while Canada and the Netherlands use the most salt.
There is relatively no difference in salt content between styles. However the can style seems to sit at the bottom of the range.

```{r}
boxplot(ramen$perc_salt ~ ramen$Country, horizontal = TRUE, las = 1, ylab = "", xlab = "Percent Salt")
boxplot(ramen$perc_salt ~ ramen$Style, horizontal = TRUE, las = 1, ylab = "", xlab = "Percent Salt")
```

**12) [Open Ended] (10 pts) You have been hired by a new ramen start up, Roamin’ Ramen. They want to better understand the ramen market and ask you to break down ramen into 5 collections of “similar” ramens. How do you go about it? Discuss what you find.**

The most efficient way to break down the ramen data is to split it into 5 collections of styles. These collections are based in frequencies. Precisely, the 5 styles are (1) Bowl, (2) Cup, (3) Pack, (4) Tray, and (5) Miscellaneous (which includes Bar, Box, and Can).

```{r}
plot(ramen$Style)
```

**13) [Open Ended] (10 pts) Roamin’ Ramen wants to make the next Top Ten Ramen winner. What recommendations do you have for them based on this data set? Be sure to use the columns provided, and generate your own ideas by examining the Variety column. Support your assertions with statistics (like mean, min, max or others you prefer) and at least one plot.**

*Note: Variety anhalysis is no longer necessary*

Our recommendations for Roamin' Ramen is to create a ramen which has a salt content of between 15.90 and 21.87 percent of the total ramen contents. We see by looking at the graph that the vast majority of 5 star ratings are given to ramens whose salt contents sit between this range, with an average of 18.43 percent salt. This evidence, along with the conclusion from question (10), that the higher salt percentage, the better rating of ramen, supports our suggestion.

```{r, echo=TRUE}
plot(ramen$Stars, ramen$perc_salt)
summary(ramen$perc_salt[which(ramen$Stars == 5)])
```
